A Flux Scale for Southern Hemisphere 21cm EoR Experiments

### 2013-04-24 ms.tex
More organization.  created sections "results and discussion" and "conclusion" and divided existing text among these.

In order to ensure that errors in
the beam model did not skew our result, we chose a set of sources near in declination
to Pictor A that would follow nearly identical tracks through the primary beam.
A list of these 
sources is given in Table \ref{tab:src_spec}. 
These sources were chosen on the basis of brightness and
proximity in declination to Pictor A.
% XXX specific declination range
% XXX merge this with paragraph below

To provide a basis for establishing the accuracy of the Pictor measurement we
measured more sources.  Specifically, we choose sources from the Molonglo
Reference Catalog \cite[MRC]{Large:1981p7798} that are within 5\arcdeg in
declination of a common calibrator (J2331-416) and have a flux extrapolated
from 408MHz greater than 10Jy assuming a power law spectral index of
-1.\footnote{Most radio sources in this band have power law spectra $S(\nu) =
\left(\frac{\nu}{\nu_0}\right)^\alpha$.  The 5\arcdeg distance between source
and calibrator was chosen as a balance between number of sources included and
the known smoothness of the beam.   The average spectral index for radio
sources in this band is $-0.8$.} This selection contains 62 sources in a narrow
stripe that passes through the majority of the southern EoR fields, much of the
galaxy and Centaurus A.

% XXX equation for time-dependent beam amplitude times source flux for perceived flux density

To derive a source spectrum from each drift-scan source profile, we compute a weighted average using
weights derived from a model of
PAPER's primary beam response as an effective approximation of inverse-variance weighting
\citep{pober_et_al2012}, and averaging over the time series for each source.  Each output source spectrum
represents a best estimate given the limitations of the beam model and flux calibration that were established
up to this point.  To further improve these estimates, we derive an additional frequency-dependent gain parameter,
smoothed on 10-MHz scales,
that brings the spectrum of J2331-416 into closest agreement with a power-law spectrum
that represents the best fit to measurements below 1 GHz.
This additional gain factor was applied to all measured spectra, including that
of Pictor A.  The expectation is that, since all sources at similar declinations follow similar tracks 
through the PAPER beam, any errors present in the original measured spectra as a result of differences between
the simulated and actual beam response should be absent in the ratio between source spectra, and therefore
should be corrected by the applied gain factor.

Finally,
the flux scale is set
by Monte Carlo fitting to a subset of sources, all of which are calibrated to
the Baars et al scale. 
% XXX elaborate on this, more on Baars, less on MC

@@

@@

% XXX incorporate
We use data observed on JD2455747 
from a 64-antenna single-polarization deployment of the 
PAPER array in a minimum redundancy configuration that is more suited for imaging.  The details
of these observations and their calibration are given in \citet{pober_et_al2013}.

%COMPRESSION
\textbf{Compression}\\

@@

%CALIBRATION
\textbf{Per-Antenna Gain and Phase Calibration}\\

@@

\textbf{Beamforming}\\

@@

%BANDPASS CALIBRATION
\textbf{Spectral calibration}\\
\label{sec:Calibration}

@@

\textbf{Catalogs}\\

Data for prior comparison was pulled from two major sources. Catalog values for
Pictor A, and the flux calibration sources were pulled directly from the
NASA/IPAC Extragalactic Database (NED)
\footnote{\url{http://ned.ipac.caltech.edu/}}. Cross-matching radio sources
between bands is made difficult by changes in resolution, spectral curvature,
and resolved multi-scale structure.  For a small number of sources these
problems can be ameliorated by inspection of the spectra, source names,
coordinates,  and originating publications. However for a large sample of
sources this becomes unwieldily and prone to error. Thus for the larger number
of samples we make use of the Vollmer et al meta-catalog which takes pains to
match multi-wavelength observations \citep{Vollmer:2010p6422}.
% given the known source dimensions and spectral properties as well as telescope bandwidth and spatial resolutions.

\textbf{Flux Scale}\\
\label{sec:flux_scale}

@@

 \section{Spectral Results}
 \label{sec:fits}

The primary purpose of this observation is to produce a high quality Pictor A
% XXX need to coordinate "primary purpose" here with abstract and intro motivation
spectrum. As a verification measure we have observed many other sources at the
same declination for comparison against previous observations.  Our comparison
metric will be the degree to which the PAPER data are consistent with previous
observations,given a model and, if consistent, they improve on the precision of
our spectral model parameters.

@@

@@

 \section{Discussion and Conclusions}
 \label{sec:Conclusion}

@@

% XXX need more discussion

>>>>

To begin, we choose sources from the Molonglo
Reference Catalog \cite[MRC]{Large:1981p7798} that are within 5\arcdeg in
declination of a common calibrator (J2331-416) and have a flux extrapolated
from 408MHz greater than 10Jy assuming a power law spectral index of
-1.\footnote{Most radio sources in this band have power law spectra $S(\nu) =
\left(\frac{\nu}{\nu_0}\right)^\alpha$.  The 5\arcdeg distance between source
and calibrator was chosen as a balance between number of sources included and
the known smoothness of the beam.   The average spectral index for radio
sources in this band is $-0.8$.} This selection contains 62 sources in a narrow
stripe that passes through the majority of the southern EoR fields, much of the
galaxy and Centaurus A.
A list of these 
sources is given in Table \ref{tab:src_spec}.

For these sources, spectral data measured below XXX GHz were compiled from 
the NASA/IPAC Extragalactic Database (NED)
\footnote{\url{http://ned.ipac.caltech.edu/}}. Cross-matching radio sources
between bands is made difficult by changes in resolution, spectral curvature,
and resolved multi-scale structure.  For a small number of sources these
problems can be ameliorated by inspection of the spectra, source names,
coordinates,  and originating publications. However for a large sample of
sources this becomes unwieldily and prone to error. Thus for the larger number
of samples we make use of the Vollmer et al meta-catalog which takes pains to
match multi-wavelength observations \citep{Vollmer:2010p6422}.
% given the known source dimensions and spectral properties as well as telescope bandwidth and spatial resolutions.

To derive a source spectrum from each drift-scan source profile, we compute a weighted average using
weights derived from a model of
PAPER's primary beam response as an effective approximation of inverse-variance weighting
\citep{pober_et_al2012}, and averaging over the time series for each source.  Each output source spectrum
represents a best estimate given the limitations of the beam model and flux calibration that were established
up to this point, according to the equation:
% XXX equation for time-dependent beam amplitude times source flux for perceived flux density
To further improve these estimates, we derive an additional frequency-dependent gain parameter,
smoothed on 10-MHz scales,
that brings the spectrum of J2331-416 into closest agreement with a power-law spectrum
that represents the best fit to measurements below 1 GHz.
This additional gain factor was applied to all measured spectra, including that
of Pictor A.  The expectation is that, since all sources at similar declinations follow similar tracks 
through the PAPER beam, any errors present in the original measured spectra as a result of differences between
the simulated and actual beam response should be absent in the ratio between source spectra, and therefore
should be corrected by the applied gain factor.

Finally,
an absolute flux scale is set
by Monte Carlo fitting to a subset of sources, all of which are calibrated to
the Baars et al scale. 
% XXX elaborate on this, more on Baars, less on MC

@@

\subsection{Observations}

@@

%COMPRESSION
\subsection{Data Compression}

@@

%CALIBRATION
\subsection{Per-Antenna Gain and Phase Calibration}

@@

\subsection{Beamforming}

@@

%BANDPASS CALIBRATION
\subsection{Bandpass Calibration}
\label{sec:Calibration}

@@

\subsection{Approximating an Absolute Flux Scale}
\label{sec:flux_scale}

@@

\subsection{Fitting a Power-Law Model to Spectra}

% XXX write this

@@

\section{Results and Discussion}
\label{sec:fits}

@@

% XXX comparison with previous in-band results (danny 2011, williams 2012)

 \section{Conclusion}
 \label{sec:Conclusion}

% XXX adapt this paragraph to be a summary of the broad goals attained in this paper
The primary purpose of this observation is to produce a high quality Pictor A
% XXX need to coordinate "primary purpose" here with abstract and intro motivation
spectrum. As a verification measure we have observed many other sources at the
same declination for comparison against previous observations.  Our comparison
metric will be the degree to which the PAPER data are consistent with previous
observations,given a model and, if consistent, they improve on the precision of
our spectral model parameters.

@@

% XXX looking to the future, what next
